An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-26 article.tex
Added a comment about missing section in methods.
first paragraph of coefficient subsection

@@

\subsection{Exploratory Analysis}

@@

@@

The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).

>>>>

\subsection{Significant Tests}
%This briefly needs to be described. You use the results of significance tests in the results section and talk about variables significance but do not describe it in the methods.
% F-tests
% T-tests

@@

\subsection{Exploratory Analysis} \label{sec:exp_anal}

@@

% Coefficients are important as they describe the direct relationship between a variable and its response. They indicate whether it is a positive, or negative relationship and the magnitude of this relationship.
The coefficients of each model describe the relationship of a predictor variable to its response when considering all other predictor variables. Due to the transformations of the data, coefficients are individually interpreted in the same manner as the prior regression values were (section\ref{sec:exp_anal}); although all coefficients need to be considered together. Unlike the regression values the coefficients range is not limited between -1 and 1, as the ratio of each variables contribution needs to be considered together.
%The dimensionless nature of these variables each coefficient refers to its own variable's distribution's standard deviations.
We look at the categorical variables' and continuous variables' coefficients separately. This is primarily done as the categorical variables have many coefficients, one for each category, whilst continuous variables have only one. The coefficient for categorical variables are summarised in Figure\ref{fig:violin}. The continuous variables coefficients are summarised in Table\ref{tab:contvar}.

@@

%The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).
